A generalization of the Bradley-Terry model for draws in chess with an application to collusion

### 2021-01-18 inst/skating_analysis.Rmd
get rid of that stupid 'misslast' argument
use skating_analysis.Rmd to create data/skating.rda

This document analyses strengths of the competitors in the Ladies'
Figure Skating at the 2002 Winter Olympics.  In the package, dataframe
`skating_table` is copied from Lock and Lock (see skating.Rd for more
details).

```{r,showskating}
set.seed(0)
data("skating")
skating_table
```

@@

```{r,convertordertosupport}
head(ordertable2supp(skating_table,misslast=FALSE))
```

@@

```{r,maxshow, cache = TRUE}
(m <- maxp(skating))
```

@@

```{r}
o <- ordertable2supp(o,misslast=FALSE)
o
```
and have some fun with it:

@@

>>>>

This document analyses strengths of the competitors in the Ladies'
Figure Skating at the 2002 Winter Olympics.  In the package, dataframe
`skating_table` is copied from Lock and Lock (see skating.Rd for more
details).  It also creates file `data/skating.rda` which contains R objects `skating_table`,

```{r,showskating}
set.seed(0)
skating_table <- read.table("skating.txt",header=TRUE)
```

@@

```{r,convertordertosupport}
head(ordertable2supp(skating_table))
```

@@

```{r,maxshow, cache = TRUE}
skating <- ordertable2supp(skating_table)
skating_maxp <- maxp(skating)
m <- skating_maxp # for ease of  typing
```

@@

```{r}
o <- ordertable2supp(o)
o
```
and have some fun with it:

@@

### Package dataset

Following lines create `skating.rda`, residing in the `data/` directory of the package.

```{r,label=saveskatingdataset}
save(skating_table,skating,skating_maxp,file="skating.rda")
```
